A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-14 MSRChallenge2016.tex
Spellcheck and update ISBN
Fixed margin violations

% ISBN
\isbn{123-4567-24-567/08/06}

@@

A considerable proportion of these works target programs written in C.
Indeed, researchers targeting Java often start from or compare against
Java-based implementations of techniques originally
implemented for C~\cite{nopol,kim2013}. % Even PAR~\cite{kim2013}, perhaps the
% best-known previously-proposed Java-based program repair technique, both starts
% from and is directly compared to a Java implementation of GenProg~\cite{genprog}, which
% targets the C programming language.  
%
This is an oversight because Java and C are very different languages.
Consider GenProg~\cite{legoues2012}, which
combines statement-level mutations into patches to address a particular
defect. Which ``Statements'' (a semantic unit in C) should be manipulated in Java?
Can we learn
intelligent rules to inform candidate modifications
(cf. Prophet~\cite{Long2016}, for C)?  What types of semantic scoping
should limit mutations, given the relative stringence of the Java
compiler?

@@

First, we broadly characterize bug-fixing commits to Java code.  In this paper,
we study the \emph{September 2015/Github} dataset on Boa, including $554,864$
Java projects with $23,229,406$ revisions. Boa identifies $4,590,679$ as bug
fixing.

@@

%\vspace{1ex}
\noindent
 {\bf Adding an array out of bound checker (AOB)}. This pattern inserts a condition to check that an array
    index is within bound right before the index is used.
%	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}.
 We count the number of if conditional expression that
  contains {\em expr<var.length} or {\em var.length>expr} for both pre- and
  post-fix version. If there is a larger count in post-fix version, we consider that an instance of the AOB pattern is found.

@@

An important study that complements ours is the repair model approach
proposed by Martinez and Monperrus~\cite{Martinez:2015ez}, which proposes
a probability distribution suggesting when to apply which kind of edit. Although their
approach is able to trace more fine-grain AST-level changes, our results are
consistent with their findings. For example, their empirical
analysis~\cite{Martinez:2015ez} shows that method invocations, if statements,
and variable declarations are added/deleted/updated most often, which
is also illustrated in Figure~\ref{fig:StmtType} (Boa groups method invocations and
variable declarations into the $\mathtt{Expression}$ category).  Our study
complements there at a much larger scale (we study 380,125 repositories with 23,229,406
revisions as compared to the 14 repositories in the prior work).

@@

\section{Acknowledgements}

>>>>

% ISBN
\isbn{978-1-4503-4186-8}

@@

A considerable proportion of these works target programs written in C.
Indeed, researchers targeting Java often start from or compare against
Java-based implementations of techniques originally
implemented for C~\cite{nopol,kim2013}. % Even PAR~\cite{kim2013}, perhaps the
% best-known previously-proposed Java-based program repair technique, both starts
% from and is directly compared to a Java implementation of GenProg~\cite{genprog}, which
% targets the C programming language.  
%
This is an oversight because Java and C are very different languages.
Consider GenProg~\cite{legoues2012}, which
combines statement-level mutations into patches to address a particular
defect. Which ``Statements'' (a semantic unit in C) should be manipulated in Java?
Can we learn
intelligent rules to inform candidate modifications
(cf. Prophet~\cite{Long2016}, for C)?  What types of semantic scoping
should limit mutations, given the relative stringency of the Java
compiler?

@@

First, we broadly characterize bug-fixing commits to Java code.  In this
paper, we study the \emph{September 2015/Github} dataset offered by Boa, including
$554,864$ Java projects with $23,229,406$ revisions. Boa identifies $4,590,679$
as bug fixing.

@@

%\vspace{1ex}
\noindent
 {\bf Adding an array out of bound checker (AOB)}. This pattern inserts a
 condition check to check that an array
    index is within bound right before the index is used.
%	{\bf Example:} arr[idx]=0 $\rightarrow$ if(idx<arr.length){arr[idx]=0}.
 We count the number of if conditional expression that
  contains {\em expr<var.length} or {\em var.length>expr} for both pre- and
  post-fix versions. If there is a larger count in post-fix version, we consider that an instance of the AOB pattern is found.

@@

An important study that complements ours is the repair model approach proposed
by Martinez and Monperrus~\cite{Martinez:2015ez}, which proposes a probability
distribution suggesting when to apply which kind of edit. Although their
approach can trace more fine-grain AST-level changes, our results are
consistent with their findings. For example, their empirical
analysis~\cite{Martinez:2015ez} shows that method invocations, if statements,
and variable declarations are added/deleted/updated most often, which is also
illustrated in Figure~\ref{fig:StmtType} (Boa groups method invocations and
variable declarations into the $\mathtt{Expression}$ category).  Our study
complements there at a much larger scale (we study 380,125 repositories with
23,229,406 revisions as compared to the 14 repositories in the prior work).

@@

\section{Acknowledgments}
